\documentclass[12pt, a4paper, oneside]{article}
  \usepackage[margin=2cm]{geometry}
  \usepackage[utf8]{inputenc}
  \usepackage{lipsum}
  \usepackage{lastpage}
  \usepackage{secdot}
  \usepackage{minted}
  \usepackage{amsmath}
  \usepackage{parskip}  
  \usepackage{fancyhdr}
  \usepackage{enumerate}
  \usepackage[shortlabels]{enumitem}
  \usepackage{graphicx}
  \graphicspath{ {images/}} 
  
  % Definitionen auf neuer Zeile
  \setdescription{labelsep=\textwidth}
    
  % Define 'variables'
  \newcommand{\noteDate}{2017-09-22}
  \newcommand{\subjectIdentifier}{BZG3401}
  \newcommand{\subject}{English}
  
  % Set header and footer content
  \pagestyle{fancy} 
  \fancyhead[L]{Severin Kaderli} 
  \fancyhead[C]{\subject{}}
  \fancyhead[R]{\noteDate{}}
  \fancyfoot[C]{}
  \fancyfoot[R]{Seite \thepage{} von \pageref{LastPage}}
  
  % Adjust width of header and footer line
  \renewcommand{\headrulewidth}{1pt}
  \renewcommand{\footrulewidth}{1pt}
  
  % Move title up and don't show date
  \title{\vspace{-1.5cm}\subjectIdentifier{}\\\subject{}}
  \author{\vspace{-1.5cm}}
  \date{\vspace{-1.5cm}}
  
  \begin{document}
  \maketitle
  \thispagestyle{fancy}
  
  % Actual content
  \section{Modulinformationen}
  {\bf Dozent}: Derek Doucette\\
  {\bf Kursunterlagen}: https://moodle.bfh.ch/course/view.php?id=15686\\
  
  \section{Verb tenses}

  \newpage
  \section{Unit 1: Social media}
  \subsection{Grammar Focus}
  
  Match the descriptions of the tenses a-f with the statements 1-6 in the text.
  \begin{enumerate}[a)] 
    \item 6 - past simple
    \item 1 - past continous
    \item 3 - present simple
    \item 5 - present perfect
    \item 4 - present perfect continous
    \item 2 - present continous
  \end{enumerate}

  Look at the tweets (a-d) from Kimball to his followers. textit all the tenses that refer to the future. Circle the best answer to describe why this form is used in sentences a-d.
  \begin{enumerate}[1.]
    \item ii
    \item iii
    \item i
    \item iii
  \end{enumerate}

  \subsection{Grammar Ex.  4}
  Complete the questions. Change the verb forms if necessary.

  \begin{enumerate}[1.]
    \item How long have you sold créme brûées?
    \item What did you do before starting your own business?
    \item Why did you start the business?
    \item How did the business get its name?
    \item What's the biggest challenge (of) running this type of business?
    \item What advantage does your business have over a traditional restaurant?
    \item What inspires you to create varied menus?
    \item What is your advice for anyone starting their own food truck?
  \end{enumerate} 

  \subsection{Grammar Ex. 5}
  \begin{enumerate}[1.]
    \item have never tasted
    \item were
    \item am meeting
    \item I'm going to choose
    \item I'll go
    \item I'll see
  \end{enumerate}

  \subsection{Grammar Ex. 8}
  \begin{enumerate}[1.]
    \item Desk phones and email
    \item They are crucial for productivity at work
    \item Instant messaging and social media
    \item For brainstorming and planing
    \item For complicated decision making
    \item Smartphones
    \item In their free time
    \item To attract the younger generation
  \end{enumerate}

  \subsection{Grammar Ex. 9}
  \begin{enumerate}[1.]
    \item true 
    \item false, about 60\%
    \item false, has increased
    \item true
    \item false
    \item true
  \end{enumerate}


  \subsection{Vocabulary Ex. 2}
  \begin{enumerate}[1.]
    \item Poor language skills lead to inaccurate \& incomplete information and miscommunication.
    \item Takes a lot of time and money.
    \item Less mobility \& job possibilities.
    \item The lack of language skills and different cultures.
    \item He ordered that everyone speaks English.
    \item With financial support.
    \item Take extra language lessons.
  \end{enumerate} 

  \subsection{Vocabulary Ex. 4 \& Ex. 5}
  \begin{center}
    \begin{tabular}{|l|l|l|l|}
      \hline
      & Prefix & Article & More examples \\ \hline
      1 & in- & efficient, accurate & convenient, direct  \\ \hline
      2 & mono- & lingual & rail, culture \\ \hline
      3 & un- & likely & happy, comfortable \\ \hline
      4 & bi- & lingual & monthly, annually \\ \hline
      5 & dis- & advantage & connect, honest \\ \hline
      6 & multi- & natiional & racial, tasking \\ \hline
      7 & mis- & understandings & calculate, use \\ \hline
      8 & over- & worked & ambitious, confident \\ \hline
      9 & im- & possible & practical, personal \\ \hline
      10 & under- & performing & paid, estimate \\ \hline
    \end{tabular}
  \end{center}

  \subsection{Vocabulary Ex. 6}
  \begin{enumerate}[1.]
    \item underperforming
    \item uncomfortable
    \item inconvenient
    \item overworked
    \item misunderstood
    \item multilingual
    \item biannual
    \item monocultural
    \item disadvantage
    \item impersonal
  \end{enumerate}

  \subsection{Dialog} 
  \begin{enumerate}[1.] 
    \item Hi I'm Evan. Nice to meet you!
    \item No, it's my first time attending one of these.
    \item Yeah, it's cool to meet all the people from all over the world.
    \item I work at the Los Angeles office. So I didn't need to travel a long distance.
    \item Yes, it's amazing. The weather is almost sunny all year around. How was your journey?
    \item That's awful!
    \item Yes, it's an amazing selection. There's lot of foods I haven't even heard of.
    \item I work in the Sales department
    \item I don't, who is she?
    \item I haven't managed to meet anyone from the head office so far.
    \item Not for very long, just for a month.
    \item Sure, I'd like to meet her.
    \item Ok, thank you very much.
    \item No thanks, I'm fine.
    \item See you later!

  \end{enumerate}

  \subsection{Customs and culture}
  \begin{enumerate}[1.]
    \item Roses as a gift is a little bit strange.
    \item Edinburgh isn't in England. Check your facts!
    \item Tables aren't for sitting.
    \item He should be equal to everyone and shake hands with everybody.
    \item She needs to use a tissue for blowing her nose or go to the bathroom.
    \item During Ramadan you shouldn't be drinking during the day.
  \end{enumerate}

  \subsection{Review: Grammar Ex. 1}
  \begin{enumerate}[1.]
    \item was studying
    \item was working
    \item adored
    \item wasn't being met
    \item launched
    \item lay
    \item had
    \item got
    \item reached
    \item were working
    \item sold
  \end{enumerate}

  \subsection{Review: Grammar Ex. 2}
  \begin{enumerate}[1.]
    \item I've taken on
    \item it is growing
    \item we launched
    \item have worked, I'm going to
    \item we do, are just doing
    \item have been living, will stay
  \end{enumerate}

  \subsection{Review: Vocabulary Ex. 1}
  \begin{enumerate}[1.]
    \item underpaid
    \item unambitious
    \item monolingual
    \item overestimate
    \item disconnect
    \item misunderstand
    \item inconvenient
    \item impossible
    \item biannual
    \item multitask
  \end{enumerate}

  \subsection{Review: Vocabulary Ex. 2}
  \begin{enumerate}[1.]
    \item misunderstood
    \item multitask
    \item biannual
    \item disconnected
    \item overestimated
    \item underpaid
    \item unambitious
    \item monolingual
    \item inconvenient
    \item impossible
  \end{enumerate}

  \subsection{Review: Work skills Ex. 1}
  \begin{enumerate}[1.]
    \item e
    \item b
    \item d
    \item a
    \item c
  \end{enumerate}

  \subsection{Review: Work skills Ex. 2}
  \begin{enumerate}[1.]
    \item How about you?
    \item The photographer. That's great.
    \item Absolutely. It must be very satisfying.
    \item And you?
    \item Were you working in Sales in your previous company then?
    \item Really! So you must enjoy it.
    \item So what attracted you to work here?
  \end{enumerate}

  \subsection{Review: Functions Ex. 1}
  \begin{enumerate}[1.]
    \item must be
    \item nice too meet you
    \item to find us OK
    \item introduce you to
    \item you know
    \item like to introduce you to
    \item this is
    \item Nice to meet you
    \item I'll look forward to
  \end{enumerate}

  \newpage
  \section{Unit 2: Resources}
  \subsection{Grammer Ex. 1}
  \begin{enumerate}[1.]
    \item Hectares of land that have been bought.
    \item For growing crops like vegetables, rice, wheat, lentils, flowers and sugar cane.
    \item Governments, global agribusinesses, investment banks, hedge funds and other financial institutions.
    \item The investment costs are very low and unregulated.
    \item They used to farm, hunt and gather and the land and it's now changing their way of life.
  \end{enumerate}

  \subsection{Grammer Focus}
  Match the sentences 1-3 with the tenses a-c.
  \begin{enumerate}[1.] 
    \item b
    \item c
    \item a
  \end{enumerate}

  Find one more example of each verb for min the article in Grammer Ex. 2.
  \begin{enumerate}[a.)]
    \item There has been an increase in demand...
    \item ... and individuals have been investing...
    \item ... 60 million hectares of land have been bought...
  \end{enumerate}

  Complete the rules.
  \begin{enumerate}[1.]
    \item past, present
    \item present perfect
    \item present perfect continuous
    \item stative
    \item present perfect passive
  \end{enumerate}

  \subsection{Grammer Ex. 3}
  \begin{enumerate}[1.]
    \item has been created
    \item has provided
    \item have been offering
    \item reported
    \item have been highlighting
    \item has reached
    \item has found
    \item announced
    \item has been put
    \item hasn't finished
    \item has been done
  \end{enumerate}

  \subsection{Work Skills Ex. 1}
  \begin{enumerate}[1.]
    \item They lost time and spent a further week finding new filming locations that were safe. In the end they only had one week for filming.
    \item Jeremy suggests if the filmed material is not enough the company can use archive material from the last year.
  \end{enumerate} 

  \subsection{Work Skills Ex. 2}
  \begin{enumerate}[a.]
    \item 4
    \item 5
    \item 1
    \item 2 
    \item 3
  \end{enumerate}

  \subsection{Review: Grammar Ex. 1}
  \begin{enumerate}[1.]
    \item Have you seen
    \item haven't had
    \item managed
    \item have been
    \item spoke
    \item has been talking
    \item have introduced
    \item met
    \item have been studying
    \item have had
  \end{enumerate}

  \subsection{Review: Grammar Ex. 2}
  \begin{enumerate}[1.]
    \item I've been for Pete for seven years.
    \item She has been wir the company since spring last year.
    \item We've benn working on this project since last Thursday.
    \item I have been a Project Manager for ITS since January 2012.
    \item I've been cycling into work since the train strike started.
    \item I've been communicating with her regularly since my US visit last year.
    \item They've been working on the building since Christmas but they're only half finished.
  \end{enumerate}

  \subsection{Review: Grammar Ex. 3}
  \begin{enumerate}[1.]
    \item f
    \item g
    \item c
    \item e
    \item a
    \item d
    \item b
  \end{enumerate}

  \subsection{Review: Vocabulary Ex. 1}
  \begin{enumerate}[1.]
    \item forced
    \item ban on
    \item permitted
    \item restricted
    \item be permitted
    \item you have no obligation
    \item to be prohibited
    \item allow their residents to carry a gun
  \end{enumerate}

  \subsection{Review: Vocabulary Ex. 2}
  \begin{enumerate}[1.]
    \item prevent 
    \item restrict
    \item reduce
    \item banned
    \item allow
    \item permitted
  \end{enumerate}

  \subsection{Review: Work skills Ex. 1}
  \begin{enumerate}[1.]
    \item Title
    \item Introduction
    \item Main points
    \item Causes of population decline
    \item Reccomendations
  \end{enumerate}

  \subsection{Review: Work skills Ex. 2}
  \begin{enumerate}[a.]
    \item describes
    \item involved
    \item provides
    \item There has been
    \item reasons
    \item Finally
    \item recommend
    \item secondly
  \end{enumerate}

  \subsection{Review: Functions Ex. 1}
  \begin{enumerate}[1.]
    \item In other words
    \item do you mean
    \item Are you with me?
    \item are you saying
    \item if I follow you
    \item Is that clear?
  \end{enumerate}

  \subsection{Review: Functions Ex. 2}
  \begin{enumerate}[1.]
    \item Are you saying
    \item I'm not sure if I follow you
    \item Are you with me?
    \item I mean
    \item What I mean
  \end{enumerate}

  \newpage
  \section{Unit 3: Work-life balance}
  \subsection{Grammar Ex. 3}
  \begin{enumerate}[1.]
    \item great sustainability \\
    great education and health \\
    gender equality \\
    a thriving export market \\
    no army
    \item six hours of sleep \\
    a 20 minute commute \\
    time with family and friends \\
    spending time outdoors \\
    get off work at a decent time
  \end{enumerate}

  \subsection{Grammar Ex. 4}
  \begin{enumerate}[1.]
    \item Yes. For me free time is a major factor in hapiness.
    \item They defined hapiness as the "degree to which an individual judges the overall quality of his or her life as a whole favourably".
    \item We also have a very good education system.
    \item It's pretty similiar. I want to have more than 6 hours sleep a night though.
  \end{enumerate}

  \subsection{Grammar Ex. 5}
  We rank pretty high I think. This is because we have a great education, enough jobs for the people and we have enough resources for us.


  \subsection{Grammar Focus}
  \begin{enumerate}[1.]
    \item a
    \item b
  \end{enumerate}

  The relative pronoun can be omitted in sentence 1.

  \textbf{Clauses for extra information:}  which has proved positive..., which commissioned..., which in the case..., who obviously appreciate...\\
  \textbf{Relative pronouns:} who, which, that, where, whose


  \subsection{Grammar Ex. 8}
  \begin{enumerate}[1.]
    \item A recent survey on hapiness, which was carried out in 149 countries, ranked countries in terms of their level of hapiness.
    \item Costa Rica, which was ranked as the happiest country, has placed great emphasis on sustainability.
    \item Education and health are areas which the Costa Ricans have invested in.
    \item Togo and Tanzania, which the survey revealed to be the least happy nations, both have relatively low GDPs.
    \item Spending time with relatives is one of the key factors that contributes to hapiness in Britain according to the survey.
    \item The 4'000 adults who took part in the survey, were asked to rate their hapiness on a scale of one to five.
    \item The research showed that those adults who work less than eight hours a day are happiest.
    \item The people who the study identified as the happiest spend about two hours a day playing with their children.
  \end{enumerate}

  \subsection{Grammar Ex. 9}
  \begin{enumerate}[1.]
    \item Hapiness, which can be defined in many ways, relates...
    \item Spending time with loved ones, which includes time spent with friends, is a key factor...
    \item Sam gave an excellent presentation last week at Reading University, where she was a student.
    \item Tim's been offered a new job in marketing, which he's been waiting for for a long time.
    \item Dr Laurel Edmunds, who has researched the issue of hapiness at work for some time, has produced a unique definition of happiness.
    \item Last month we conducted a staff survey, whose results are due out this week.
    \item Maslow's motivation theory, which is perhaps the best-known theory of hapiness, can be representated by a visual aid shaped like a pyramid.
    \item Job satisfaction, which is frequently measured by companies and organizations, is a very important aspect of people's working lives.
  \end{enumerate} 

  \subsection{Grammar Ex. 10}
  \begin{enumerate}[1.]
    \item Norway, which is at the top of the happiness index, has a relatively mediocre income per head.
    \item Togo, which is at the bottom of the happiness index, has the lowest income per head.
    \item Luxemburg, which has the highest income per head, is near the top of the hapiness index.
    \item Brazil, which has a relatively low income per head, is about in the center of the hapiness index.
  \end{enumerate}

  \subsection{Vocabulary Ex. 4}
  \begin{enumerate}[1.]
    \item productivity
    \item reality
    \item responsibility
    \item employee
    \item cooperation
    \item satisfaction
    \item motivation
    \item managerial, managing, managable
    \item social
    \item stimulating
    \item creative
    \item enjoyable
    \item neccesary
    \item serious
  \end{enumerate}

  \subsection{Vocabulary Ex. 6 \& 7}
  \begin{center}
    \begin{tabular}{|l|l|l|l|}
      \hline
      & Suffix & Nouns / Adjectives & Examples \\ \hline
      1 & -ity & Nouns & reality, creativity, necessity, \textit{opportunity} \\ \hline
      2 & -ive & Adjectives & cooperative, creative, \textit{informative} \\ \hline
      3 & -ible & Adjectives & responsible, \textit{sensible} \\ \hline
      4 & -able & Adjectives & enjoyable, employable, \textit{favourable} \\ \hline
      5 & -tion & Nouns & motivation, stimulation, \textit{exception} \\ \hline
      6 & -ment & Nouns & enjoyment, \textit{entertainment} \\ \hline
      7 & -ing & Adjectives & managing, stimulating, \textit{exciting} \\ \hline
      8 & -al & Adjectives & real, \textit{critical}, \textit{additional}, \textit{inspirational} \\ \hline
      9 & -ous & Adjectives & serious, \textit{nervous}, \textit{cautios} \\ \hline
    \end{tabular}
  \end{center}

  \subsection{Vocabulary 8}

  \subsection{Vocabulary 9}

  \subsection{Vocabulary 10}

  \subsection{Functions Ex. 2}
  \begin{enumerate}[1.]
    \item He's researching problems with the project.
    \item With a summary of the project.
    \item Getting enough natural light on the deepest levels. Greenhouse effect because of the glass roof. Difficult conditions for constructing because of the wet earth.
    \item Possibly, with some expensive technological investment.
    \item Most likely not. There are a lot of problems that need to be solved which will cost quite a bit of money.
  \end{enumerate}

  \subsection{Functions Focus}
  \begin{enumerate}[1.]
    \item hedging
    \item contrasting
    \item generalizing
  \end{enumerate}

  \subsection{Functions Ex. 3}
  \begin{enumerate}[1.]
    \item apparently
    \item Perhaps
    \item It seems
    \item I'm not sure, apparently
    \item it's not clear
    \item Apparently
  \end{enumerate}

\end{document} 